### 2016-11-10 paper/evaluation.tex
Updated parallel modes
fix compile/syntax Latex error

\Jbc{Subject selection is currently OK but I will use another way (eg
Google BigQuery) to have access to more subjects.}We used the Github's
Search API~\cite{githubsearch} to fetch the top 1,000\footnote{The
Search API imposes the limit of 1,000 results regardless of the number
of matches from a search criteria.} Java projects with at least 100
stars. The number of stars indicates the interest and appreciation
from the community to a given project.
\Comment{(https://help.github.com/articles/about-stars/)} Although our
criteria is subjective, it is an approximation to find relevant
projects to conduct our study. We detected the build manager system
based on the files located in the root directory from the project in
the following precedence: Maven (\emph{pom.xml)}, Gradle
(\emph{gradlew}), and Ant (\emph{build.xml}).\Jbc{Remember to update
the following values after updating the subject selection approach.}
From the 1,000 downloaded projects, we detected the build system of
801 subjects (composed by 216 Maven, 564 Gradle, and 21 Ant projects)
and considered 164 projects that we were able to compile (153 Maven
and 9 Ant projects).  We were unable to compile other subjects because
some are related to a particular platform (\eg, Gradle implied
Android), unsolved dependencies, or the build process is based on
user-defined tasks (\eg, we considered the name \emph{compile} on Ant
projects).

@@

\begin{center}
\lstset{language=XML}
\begin{lstlisting}
 <plugin>
     <groupId>org.apache.maven.plugins</groupId>
     <artifactId>maven-surefire-plugin</artifactId>
     <configuration>
         <parallel>methods</parallel>
         <threadCount>2</threadCount>
         <perCoreThreadCount>true</perCoreThreadCount>
     </configuration>
</plugin>
\caption{\Fix{...}}
\end{lstlisting}
\label{code:surefire}
\end{center}

>>>>

\Jbc{Subject selection is currently OK but I will use another way (eg
Google BigQuery) to have access to more subjects.}We used the Github's
Search API~\cite{githubsearch} to fetch the top 1,000\footnote{The
Search API imposes the limit of 1,000 results regardless of the number
of matches from a search criteria.} Java projects with at least 100
stars. The number of stars indicates the interest and appreciation
from the community to a given project.
\Comment{(https://help.github.com/articles/about-stars/)} Although our
criteria is subjective, it is an approximation to find relevant
projects to conduct our study. We detected the build manager system
based on the files located in the root directory from the project in
the following precedence: Maven (\emph{pom.xml}), Gradle
(\emph{gradlew}), and Ant (\emph{build.xml}).\Jbc{Remember to update
the following values after updating the subject selection approach.}
From the 1,000 downloaded projects, we detected the build system of
801 subjects (composed by 216 Maven, 564 Gradle, and 21 Ant projects)
and considered 164 projects that we were able to compile (153 Maven
and 9 Ant projects).  We were unable to compile other subjects because
some are related to a particular platform (\eg, Gradle implied
Android), unsolved dependencies, or the build process is based on
user-defined tasks (\eg, we considered the name \emph{compile} on Ant
projects).

@@

### 2016-11-10 paper/modes.tex
fix compile/syntax Latex error

\Jbc{I have to understand better how Surefire executes tests. I'm
    afraid it has its own wrapper classes and reuse JUnit core
    functionalities. I'm saying this because JUnit does not offer a
    finer control over thread numbers while this configuration is
possible with Surefire} For example, Figure~\ref{fig:surefire}
illustrates how to configure Maven to execute classes sequentially
(default behavior) and test methods in parallel. Although the setting
are configured on the build file (\eg, \emph{pom.xml} on Maven}, these
settings are forwarded to the underlying testing framework (\eg,
JUnit). In case of JUnit,

>>>>

\Jbc{I have to understand better how Surefire executes tests. I'm
    afraid it has its own wrapper classes and reuse JUnit core
    functionalities. I'm saying this because JUnit does not offer a
    finer control over thread numbers while this configuration is
possible with Surefire} For example, Figure~\ref{fig:surefire}
illustrates how to configure Maven to execute classes sequentially
(default behavior) and test methods in parallel. Although the setting
are configured on the build file (\eg, \emph{pom.xml} on Maven), these
settings are forwarded to the underlying testing framework (\eg,
JUnit). In case of JUnit,
